---
title: "p8105_hw1_mgw2144"
output: github_document
date: "2023-09-19"
---

install.packages("moderndive") performed in console

```{r}
library(moderndive)
library(tidyverse)
```

```{r}
data("early_january_weather")
```

```{r}
help("early_january_weather")
```

The dataset "early_january_weather" has 15 variables: 
*   origin (weather station)
*   year, month, day, hour (time of recording)
*   temp, dewp (temperature and dewpoint in F)
*   humid (relative humidity)
*   wind_dir, wind_speed, wind_gust (wind direction (in degrees), speed and gust       speed (in mph))
*   precip (precipitation in inches)
*   pressure (sea level pressure in millibars)
*   visib (visibility in miles)
*   time_hour (date and hour of the recording)

```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
There are 358 rows and 15 columns in the dataset as assessed trough the nrow and ncol function.

```{r}
mean(early_january_weather[["temp"]])
```
The mean temperature in the dataset is 39.58 degrees fahrenheit.

Write a short description of the dataset using inline R code; accessing the dataset help file can be informative. In your discussion, please include:

the variables in this dataset, including names / values of important variables

