---
title: "p8105_hw1_mgw2144"
output: github_document
date: "2023-09-19"
---

Problem 1

install.packages("moderndive") performed in console

```{r}
library(moderndive)
library(tidyverse)
```

```{r}
data("early_january_weather")
```

```{r}
help("early_january_weather")
```

The dataset "early_january_weather" has 15 variables: 
*   origin (weather station)
*   year, month, day, hour (time of recording)
*   temp, dewp (temperature and dewpoint in F)
*   humid (relative humidity)
*   wind_dir, wind_speed, wind_gust (wind direction (in degrees), speed and gust       speed (in mph))
*   precip (precipitation in inches)
*   pressure (sea level pressure in millibars)
*   visib (visibility in miles)
*   time_hour (date and hour of the recording)

```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
There are 358 rows and 15 columns in the dataset as assessed trough the nrow and ncol function.

```{r}
mean(early_january_weather[["temp"]])
```
The mean temperature in the dataset is 39.58 degrees fahrenheit.

Write a short description of the dataset using inline R code; accessing the dataset help file can be informative. In your discussion, please include:

the variables in this dataset, including names / values of important variables

```{r}
early_january_weather %>%
  ggplot(aes(x = time_hour, y = temp, color = humid)) +
  geom_point()

ggsave("scatterplot_hw1.pdf")
```

The plot shows an increasing trend in temperature overall over the the course of the two week period. The temperature cycles up and down with the hours following the day and night cycles. There appears to be a cold period in the days approaching January 14th where the highs of the temperatures are lower and there is less spread between the highs and lows in the temperature points for the day. 


Problem 2

